\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{A Radial Time Projection Chamber for $\alpha$ detection in CLAS at JLab}

### 2018-01-18 eg6-letters/NIM/review-1/review-1.tex
Updated the review answers of NIM

\item Relevant length and thicknesses of the various elements are reported in 
   the text and in the figure, can you please add also the z position of the 
   target w.r.t the detector? To give the complete information, I would also 
   add the value of the induction gap electric field, which is the only missing 
   field value and the value of the reached amplification gain with the three 
   GEM.\\
\textcolor{blue}{ The text has been modified to clarify the z position of the 
target and the RTPC with respect to CLAS sectrometer.\\
Regarding the electric field it is unclear what you call the induction gap. We
provide these fields for the drift region and the inter-GEM regions which we 
find most relevant. If extra information is needed, please let us know.\\
The gain of such triple GEM configuration has been studied by 
CERN's Gas Detector Development Group (Fabio Sauli, Progress with the Gas 
Electron Multiplier, 2nd Workshop on Advanced Transition Radiation Detectors 
for Accelerator and Space Applications (Bari, Sept. 4-7, 2003), Nucl. Instr. 
and Meth. A522(2004)93). We evaluated only the overall gain in our chamber, 
the lack of calibration of some electronics elements makes it impossible for 
us to extract a gain specific to the GEM system at this point.}

@@

\item line 119: is the Kapton of the GEM foil really 300 mum thick? It is 
   usually very thin, like 50 mum, in order to have low material budget and 
   very high fields.\\
\textcolor{blue}{Sorry typo. It is 50 $mu$m}

@@

\subsection*{ Chapter 4}
	/paragraph 4.1
\item I would really prefer to call it drift "velocity" instead of drift 
   "speed"\\
\textcolor{blue}{What is calibrated here is mainly the drift time, based 
on your next question as well, we clarified the text about these.} 
\textcolor{red}{To be implemented}

\item I don't really understand the procedure to find the drift velocity 
   described here and fig. 7. What is $Nb_{max}$ and $Nb_{max/2}$? Why does 
   $T_{max/2}$ correspond to $Nb_{max/2}$ and why is it used as $T_{max}$? If I 
   make a quick calculation and use $T_{max}$ ~ 65 * 100ns and a drift length 
   of ~ 3cm /cos(23$^{\circ}$) ~ 7.5 cm I get a $v_{drift}$ ~ 1.15 cm/microsec 
   << 5 cm/microsec which is the average value of drift velocity in drift 
   chambers.\\
The procedure according to me would be:\\
- for each hit associated to a track, whose time information is available, take 
the drift time $t_{drift_{i}}$;\\
- plot the distribution of these $t_{drift_{i}}$;\\
- find the $T_{min}$ = minimum $t_{drift_{i}}$ and $T_{max}$ = maximum 
$t_{drift_{i}}$\\
- compute $delta_{t} = T_{max} - T_{min}$ and extract the drift velocity by 
dividing the track length / $delta_{t}$. Figure 8 would have the $delta_{t}$ 
instead of the $T_{max}$ vs z.\\
Please provide more details on the applied procedure, since I have the open 
questions I wrote before and I could not understand it properly. Moreover, 
please quote the value of the found drift velocity. Is it in accordance with 
the simulations?\\
\textcolor{blue}{The text has been updated to simplify and clarify the procedure 
(in particular, some of the variable were not necessary). What we are doing is pretty 
similar to what you describe, but we might have overlooked some informations in the
original description. Hopefully it is now better.\\
Trigger time is at time bin 15, so T = 50*100~ns = 5$\mu$s.
The drift length is equal to 3cm/ cos(23$^{\circ}$ = 3.26 cm (I assume the 7.5 is a typo).
Giving $v_{drift}$ = 0.65 cm/$\mu$s. These values are exactly what was anticipated by
our early comparison of gaz mixtures based on MAGBOLTZ, so we assume there is no 
problem there.\\} 
\textcolor{red}{Actually the text still needs some work}

@@

\item Has the stability of the drift path been counter checked with simulations 
   varying the field according to the cathode radius variation? How much is the 
   field variation if the radius have some mm of uncertainty?\\
\textcolor{blue}{We did not study this case. }

@@

\item When it says that the pad charge is "compared" to the neighboring ones, 
   what happens next? Is it the noise reduction step described later? If so, 
   please write it. \\
\textcolor{blue}{The gain extraction is following this order: \\
- pass 1: the gain of each pad is defined as the ratio between the mean 
recorded experimental ADCs to the mean simulated ADCs in the same track. Then 
for each pad, the gain ratios were collected from all the identified elastic 
tracks and these gains were fitted by a Landau function to give a
  first pass gain for each pad as the most probable value of the fit.\\
 - pass2: to make sure that the recorded ADCs by a given pad are similar to the 
 recorded ADCs by other pads in the same track, we refined this calibration. For this, 
 we compared the mean ADCs of each pad to the mean ADCs of the whole track. 
 This ratio is collected from all the elastic events and a gain correction 
 factor is extracted and applied giving a final gain for each pad.
  }

@@

\item Figure 12 - please, put it after figure 11. Moreover, please change dEdx 
   to dE/dx on y axis. Why are the left and right pictures so different?  
   Talking about the deuteron band which is present only in the left figure and 
   the smear on the top part of the right picture. \\
\textcolor{red}{The figures layout will be updated.\\}

\textcolor{blue}{The y-axis label on figure 12 is updated. Regarding the lower 
   peak in the left module of the RTPC, it is likely not deuterons. We added
   a footnote to clarify the question.}

@@

\item How was the "10 hits" cut chosen? What is the mean number of primary 
   ionization in this gas mixture?\\
   \textcolor{blue}{This cut is set to avoid tracks made out of random noise and
to limit computing time. The number of hits in good tracks at the end of the 
analysis is always above 30, with a mean around 135, so this cut has no impact 
on the good track selection.}

@@

\item Is it "high rate environment" or "high readout rate"? They are connected, 
   but what is the rate the RTPC underwent during data taking?\\
\textcolor{red}{The rate of protons is of MHz in the chamber with a readout of
about 3kHz, so one could argue that it is both. Our point here is to emphasis
the high rate however, as these slow protons deposit a lot of energy in the 
chamber.}

>>>>

\item Relevant length and thicknesses of the various elements are reported in 
   the text and in the figure, can you please add also the z position of the 
   target w.r.t the detector? To give the complete information, I would also 
   add the value of the induction gap electric field, which is the only missing 
   field value and the value of the reached amplification gain with the three 
   GEM.\\
\textcolor{blue}{ The text has been modified to clarify the z position of the 
target and the RTPC with respect to CLAS sectrometer.\\
Regarding the electric field it is unclear what you call the induction gap. We
provide the fields for the drift region and the inter-GEM regions which we 
find most relevant. If extra information is needed, please let us know.\\
The gain of such triple GEM configuration has been studied by 
CERN's Gas Detector Development Group (Fabio Sauli, Progress with the Gas 
Electron Multiplier, 2nd Workshop on Advanced Transition Radiation Detectors 
for Accelerator and Space Applications (Bari, Sept. 4-7, 2003), Nucl. Instr. 
and Meth. A522(2004)93). We evaluated only the overall gain in our chamber, 
the lack of calibration of some electronics elements makes it impossible for 
us to extract a gain specific to our GEM system at this point.}

@@

\item line 119: is the Kapton of the GEM foil really 300 mum thick? It is 
   usually very thin, like 50 mum, in order to have low material budget and 
   very high fields.\\
\textcolor{blue}{Sorry typo. It is 50 $\mu$m}

@@

\subsection*{ Chapter 4}
	/paragraph 4.1
\item I would really prefer to call it drift "velocity" instead of drift 
   "speed"\\
\textcolor{blue}{What is calibrated here is mainly the drift time, based 
on your next question as well, we clarified the text about these.}

\item I don't really understand the procedure to find the drift velocity 
   described here and fig. 7. What is $Nb_{max}$ and $Nb_{max/2}$? Why does 
   $T_{max/2}$ correspond to $Nb_{max/2}$ and why is it used as $T_{max}$? If I 
   make a quick calculation and use $T_{max}$ ~ 65 * 100ns and a drift length 
   of ~ 3cm /cos(23$^{\circ}$) ~ 7.5 cm I get a $v_{drift}$ ~ 1.15 cm/microsec 
   << 5 cm/microsec which is the average value of drift velocity in drift 
   chambers.\\
The procedure according to me would be:\\
- for each hit associated to a track, whose time information is available, take 
the drift time $t_{drift_{i}}$;\\
- plot the distribution of these $t_{drift_{i}}$;\\
- find the $T_{min}$ = minimum $t_{drift_{i}}$ and $T_{max}$ = maximum 
$t_{drift_{i}}$\\
- compute $delta_{t} = T_{max} - T_{min}$ and extract the drift velocity by 
dividing the track length / $delta_{t}$. Figure 8 would have the $delta_{t}$ 
instead of the $T_{max}$ vs z.\\
Please provide more details on the applied procedure, since I have the open 
questions I wrote before and I could not understand it properly. Moreover, 
please quote the value of the found drift velocity. Is it in accordance with 
the simulations?\\
\textcolor{blue}{The text has been updated to simplify and clarify the procedure 
(in particular, some of the variable were not necessary). What we are doing is pretty 
similar to what you describe, but we might have overlooked some informations in the
original description. Hopefully it is now better.\\
Trigger time is at time bin 15, so T = 50*100~ns = 5$\mu$s.
The drift length is equal to 3cm/ cos(23$^{\circ}$ = 3.26 cm (I assume the 7.5 is a typo).
Giving $v_{drift}$ = 0.65 cm/$\mu$s. These values are exactly what was anticipated by
our early comparison of gaz mixtures based on MAGBOLTZ, so we assume there is no 
problem there.\\}

@@

\item Has the stability of the drift path been counter checked with simulations 
   varying the field according to the cathode radius variation? How much is the 
   field variation if the radius have some mm of uncertainty?\\
\textcolor{blue}{No, we did not study this. Field variation of several \% is
   possible, but note that our data driven calibration does not depend on
   the electric field.}

@@

\item When it says that the pad charge is "compared" to the neighboring ones, 
   what happens next? Is it the noise reduction step described later? If so, 
   please write it. \\
\textcolor{blue}{ 
 The ratio is collected from all the elastic events and a gain correction 
 factor is extracted and applied giving a final gain for each pad. \\
 The noise reduction process is completely independent of the calibration
 and is performed before all other steps. We clarified the text in the article. 
  }

@@

\item Figure 12 - please, put it after figure 11. Moreover, please change dEdx 
   to dE/dx on y axis. Why are the left and right pictures so different?  
   Talking about the deuteron band which is present only in the left figure and 
   the smear on the top part of the right picture. \\
\textcolor{blue}{The figures layout is updated. The y-axis label on figure 12 
   is also updated. Regarding the lower 
   peak in the left module of the RTPC, it is likely not deuterons. We added
   a footnote to clarify the question.}

@@

\item How was the "10 hits" cut chosen? What is the mean number of primary 
   ionization in this gas mixture?\\
   \textcolor{blue}{This cut is set to avoid tracks made out of random noise and
to limit computing time. The number of hits in good tracks at the end of the 
analysis is always above 30, with a mean around 135, so this cut has no impact 
on the good track selection. We did not study the number of primary ionization, 
since we are looking at low energy $\alpha$s, we assumed it is very large. }

@@

\item Is it "high rate environment" or "high readout rate"? They are connected, 
   but what is the rate the RTPC underwent during data taking?\\
\textcolor{blue}{The rate of slow protons is of MHz in the chamber with a readout of
about 3kHz, so one could argue that it is both. However, our point there is to emphasis
the high rate, as these slow protons deposit a lot of energy in the chamber.}
